---
title: "Clean Polygon data"
author: "Anna Talucci"
date: "3/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Using part2-gee-vectors-SingleEco data file, we remove holes, convert from multipoly to polygon, apply negative buffer, and combine into single shapefile.

In GEE, vectors were run within  hotspot polygons across 3 ROI

1. Union is use to merge overlaping polygons 
  + For example, where a fire spans the imagery boundaries producing multiple polygons, these are merged into a single polygon.
2. Cast to Polygon
  + This convers from a multipolygon to individual Polygons
3. Remove Holes
  + This removes any holes created in polgyons during the GEE vectorize process, or when mergeing polygons
  + It is important to remove as holes can cause issues during geoprocesses.
4. **Vectors have too many edges to use in GEE after processing - Need to integrate a smoothing function.**



# Clear workspace

```{r}
rm(list=ls()) 
```

# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(tidyr)
library(spatialEco)
library(ggplot2)
library(nngeo)
library(rmapshaper)
library(units)
library(smoothr)
```

# Projections


Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 

```{r}
ea_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

# Read in shapefile
```{r}
E_EPoly2_1 = readOGR("../data/Part2-Vectors-HarmEA/E_EPoly2_1_ee_HarmEaFires_2020.shp", "E_EPoly2_1_ee_HarmEaFires_2020") 
NEPoly1 = readOGR("../data/Part2-Vectors-HarmEA/NEPoly1_ee_HarmEaFires_2020.shp", "NEPoly1_ee_HarmEaFires_2020") 
W_EPoly2_2 = readOGR("../data/Part2-Vectors-HarmEA/W_EPoly2_2_ee_HarmEaFires_2020.shp", "W_EPoly2_2_ee_HarmEaFires_2020") 

```



# Reproject in Equal area

```{r}
E_EPoly2_1_ee = spTransform(E_EPoly2_1, CRS(ea_russia))
NEPoly1_ee = spTransform(NEPoly1, CRS(ea_russia))
W_EPoly2_2_ee = spTransform(W_EPoly2_2, CRS(ea_russia))
```

# Buffer 
Buffer by 1000m (1km). Originally  a buffer was applied in GEE, but to maintain equal area projection we perform the buffer here at the begining to combine adjacent polygons.  
```{r}
E_EPoly2_1_buff = gBuffer(E_EPoly2_1_ee, width = 1000, capStyle="ROUND", joinStyle="ROUND")
```

```{r}
NEPoly1_buff = gBuffer(NEPoly1_ee, width = 1000, capStyle="ROUND", joinStyle="ROUND")
```

```{r}
W_EPoly2_2_buff = gBuffer(W_EPoly2_2_ee, width = 1000, capStyle="ROUND", joinStyle="ROUND")
```



# Remove holes inside polygons

```{r}
E_EPoly2_1_buff_nh = remove.holes(E_EPoly2_1_buff)
```

```{r}
NEPoly1_buff_nh = remove.holes(NEPoly1_buff)
```

```{r}
W_EPoly2_2_buff_nh = remove.holes(W_EPoly2_2_buff)
```


# Combine into one shapefile

```{r}
all_shp = rbind(E_EPoly2_1_buff_nh, NEPoly1_buff_nh, W_EPoly2_2_buff_nh)
```

```{r}
all_shp
```
```{r eval=FALSE, include=FALSE}
plot(all_shp)
```

# Apply negative buffer
```{r eval=FALSE, include=FALSE}
all_shp_nbuf = gBuffer(all_shp, width = -1000, capStyle="ROUND", joinStyle="ROUND")
```

# Convert from sp to sf
```{r}
all_shp_sf = st_as_sf(all_shp)
```

# Union overlapping  Polygons
```{r}
all_shp_un = sf::st_union(all_shp_sf)
```

# Covert from Multipolygon to Polygon
```{r}
all_shp_cast = st_cast(all_shp_un,"POLYGON")
```




# write Shapefile
```{r}
st_write(all_shp_cast, "../outputs/2.1-GEE-clean-shapefiles-EqualArea/combine1_equalarea_2020.shp", driver="ESRI Shapefile") 
```


